Choose a License

### 2024-09-18 choose_license.qmd
Fix typo

> Except otherwise noted, all files in this project are made available under CC0\ 1.0 or (at your option) under the terms of the Apache Software License\ 2.0.

>>>>

> Except where noted otherwise, all files in this project are made available under CC0\ 1.0 or (at your option) under the terms of the Apache Software License\ 2.0.
